%---------------------------------------------------------------------------%
%->> 封面信息及生成
%---------------------------------------------------------------------------%
%-
%-> 中文封面信息
%-
\confidential{}% 密级：只有涉密论文才填写
\schoollogo{scale=0.095}{ucas_logo}% 校徽
\title{BESIII实验上粲重子{$\Lambda^+_c\to\Xi^{(*)0}K^+$} 绝对衰变分支比测量及{$\lhcb$}实验上质心系能量在13{$\tev$}下{$\psitwos$}产生截面测量}
\author{李培荣}
\advisor{郑阳恒~教授,~中国科学院大学}
\advisorsec{}% 指导老师附加信息 或 第二指导老师信息
\degree{物理学}% 学位：学士、硕士、博士
\degreetype{地球}% 学位类别：理学、工学、工程、医学等
\major{粒子物理与原子核物理}
\institute{中国科学院大学物理科学学院}
\chinesedate{2018~年~7~月}% 毕业日期：夏季为6月、冬季为12月
%-
%-> 英文封面信息
%-
\englishtitle{Measurements of Absolute  Branching Fractions for {$\Lambda^+_c\to\Xi^{(*)0}K^+$} \\ at BESII and \\ Measurement of {$\psitwos$} production cross-sections at {\lhcb} at 13{$\tev$}} 
\englishauthor{Pei-Rong Li}
\englishadvisor{Prof. Yangheng Zheng}
\englishdegree{Doctor}% 学位：Bachelor, Master, Doctor。封面格式将根据英文学位名称自动切换，请确保拼写准确无误
\englishdegreetype{Natural Science}% 学位类别：Philosophy, Natural Science, Engineering, Economics, Agriculture 等
\englishthesistype{thesis}% 论文类型： thesis, dissertation
\englishmajor{Particle Physics and Nuclear Physics}% 二级学科专业名称
\englishinstitute{University of Chinese Academy of Sciences}
\englishdate{July, 2018}% 毕业日期：夏季为June、冬季为December

%-
%-> 生成封面
%-
\maketitle% 生成中文封面
\makeenglishtitle% 生成英文封面
%-
%-> 作者声明
%-
\makedeclaration% 生成声明页
%-
%-> 中文摘要
%-
\chapter*{摘\quad 要}\chaptermark{摘\quad 要}% 摘要标题
\setcounter{page}{1}% 开始页码
\pagenumbering{Roman}% 页码符号

粲重子$\lambdacp$的强子末态衰变只能通过弱相互作用发生，研究其衰变分支比对于理解弱相互作用十分重要。
基于BESIII实验在 $\sqrt{s}=4.6\gev$ 处采集的567\,pb$^{-1}$的~$\ee$~对撞数据，运用双$\Lambda_c$标记的技术首次测量了$\Lambda^+_c\to\Xi^{(*)0}K^+$的绝对分支比分别为$\mathcal{B}(\Lambda^+_c\to\Xi^0K^+)=(5.90\pm0.86\pm0.39)\times10^{-3}$~和~$\mathcal{B}(\Lambda^+_c\to\Xi(1530)^0K^+)=(5.02\pm0.99\pm0.31)\times10^{-3}$。
其中第一项误差指的是统计误差，第二项为系统误差。
这一测量是首次进行的绝对测量，且结果同之前相对测量的精度要好。

利用大型强子对撞机$\lhc$上的$\lhcb$实验在2015年收集的积分亮度为275\,pb$^{-1}$的质子-质子对撞数据，我们对$\psitwos$介子的微分产生截面进行了测量。
对于直接产生的$\psitwos$介子和来自于$b$强子衰变的$\psitwos$介子我们都测量了其在横动量范围$2<\pt<20\gevc$且快度范围$2.0<y<4.5$区间内，产生截面随着横动量$\pt$和快度$y$变化的微分截面。
在整个运动学区间内的积分截面对于直接产生的$\psitwos$介子为$\promptresult$，对于来自于$b$强子衰变的$\psitwos$介子为$\frombresult$。
其中第一项误差指的是统计误差，第二项为系统误差。
上述所有的测量结果都和理论计算吻合的很好。

\keywords{北京谱仪III，粲重子$\Lambda_c^+$，绝对分支比，$\lhcb$，$\psitwos$介子，产生截面}
%-
%-> 英文摘要
%-
\chapter*{Abstract}\chaptermark{Abstract}% 摘要标题

The hadronic decays of charmed baryon $\lambdacp$ happen only through weak interaction.
The study of its hadronic decay rates are key probes to understand the weak interactions.
We report the first measurements of absolute branching fractions for the $W$-exchange-only processes $\Lambda^+_c\to\Xi^0K^+$ and $\Lambda^+_c\to\Xi(1530)^0K^+$ with the double-tag technique, by analyzing an $e^{+}e^{-}$ collision data sample, that corresponds to an integrated luminosity of 567~pb$^{-1}$ collected at a centre-of-mass energy of 4.6~GeV by the BESIII detector.
The branching fractions are measured to be $\mathcal{B}(\Lambda^+_c\to\Xi^0K^+)=(5.90\pm0.86\pm0.39)\times10^{-3}$ and $\mathcal{B}(\Lambda^+_c\to\Xi(1530)^0K^+)=(5.02\pm0.99\pm0.31)\times10^{-3}$, where the first uncertainties are statistical and the second systematic.
These are the first absolute measurements of their branching fractions and the precisions are also improved compared with the relative measurements before.

The production cross-sections of $\psitwos$ mesons in proton-proton collisions at a centre-of-mass energy $\sqs=13\tev$ are measured with a data sample collected by the $\lhcb$ detector in the $\lhc$ operations in 2015. 
The corresponding integrated luminosity is $275\invpb$.
 The cross-sections for prompt $\psitwos$ mesons and those for $\psitwos$ mesons from $b$-hadron decays are determined as functions of the transverse momentum $\pt$ and the rapidity $y$ of the $\psitwos$ meson in the kinematic range $2<\pt<20\gevc$ and $2.0<y<4.5$.
The production cross-sections integrated over the kinematic coverage are 
$\promptresult$ 
%$1.497\pm0.004\stat\pm0.082\syst\mub$ 
for prompt $\psitwos$ mesons, and 
$\frombresult$
%$0.443\pm0.002\stat\pm0.026\syst\mub$ 
for $\psitwos$ mesons from secondary $b$-hadron decays.
The first uncertainties are statistical and the second systematic.
All measurements show good agreement with theoretical calculations.

\englishkeywords{BESIII, charmed baryon $\Lambda_c^+$,absolute branching fraction,$\lhcb$,$\psitwos$,production cross-section}

%---------------------------------------------------------------------------%
